\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary Time Series

### 2023-12-06 manuscript/manuscript.tex
Changed Figures and Added Tables

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/normal}
  \caption{A Q-Q plot of the p-values testing that a distribution
  generated from a $N(8,8)$ data generating process is normal.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/zoom_normal}
  \caption{A version of the above plot zoomed in to probabilities between 0 and
  0.1}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/gamma}
  \caption{A Q-Q plot of the p-values testing that a distribution
  generated from a $\gamma(8,1)$ data generating process is gamma distributed.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/zoom_gamma}
  \caption{A version of the above plot zoomed in to probabilities between 0 and
  0.1}
  \label{fig:mu}
\end{figure}

@@

\input{tables/rr}

@@

\subsection{Precipitation in Mansfield Connecticut}
Monthly maximums of daily precipiation in inches time series data was retrieved 
from the John F. Kennedy (JFK) International Airport station from the 
National Oceanic and Atmospheric Administration.
%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

@@

We expect the distribution of Microsoft stock returns to have a slightly
heavier tail than the normal distribution. We can test that it is normally
distributed (which we expect to reject). Then we can try testing if it follows
the $t$ distribution with different degrees of freedoms.

@@

We have shown that given a large enough sample of a time series, the block 
bootstrap KS test can appropriately fail to reject the null hypothesis when the
series follows the null distribution. It requires a larger sample size than 
basic bootstrap.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/normal}
  \caption{A Q-Q plot of the p-values testing that a distribution
  generated from a $N(8,8)$ data generating process is normal.}
  \label{fig:normal}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/zoom_normal}
  \caption{A Q-Q plot of the p-values displayed in \ref{fig:normal} zoomed in to 
  probabilities between 0 and
  0.1}
  \label{fig:zoom_normal}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/gamma}
  \caption{A Q-Q plot of the p-values testing that a distribution
  generated from a $\gamma(8,1)$ data generating process is gamma distributed.}
  \label{fig:gamma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/zoom_gamma}
  \caption{A Q-Q plot of the p-values displayed in \ref{fig:gamma} zoomed in to 
  probabilities between 0 and
  0.1}
  \label{fig:zoom_gamma}
\end{figure}

@@

\input{tables/rr_100}

From \ref{table:rr_100}, we can see that when $n = 100$, the rejection rate may 
be quite low, especially for lower values of $\alpha$. From \ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from \ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is higher for the $\gamma(8, 1)$ sample than for 
the $N(8, 8)$ As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

\input{tables/rr_200}

\input{tables/rr_400}

\input{tables/rr_800}

\input{tables/rr_1600}

\input{tables/rr_3200}

@@

\subsection{Precipitation in Mansfield Connecticut}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport, New York LaGuardia International 
Airport,
and Los Angeles International Airport stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LaGuardia and
Midway were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data is from
May 1st of 1948 to January 1st of 2014. To confirm that our method works, we 
used it to test that
the precipitation time series from each of these locations followed the 
Generalized Extreme Value (GEV) distribution.

\input{tables/precipitation_pvals}
%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

Using a significance level as high as .10 still results in a failed rejection
of the null hypothesis that all three time series follow the GEV distribution.

@@

We expect the distribution of Microsoft stock returns to have a slightly
heavier tail than the normal distribution. We can test that it is normally
distributed (which we expect to reject).  While we 
could choose to estimate a fited value of the degrees of freedom parameter as
part of our method, it is very difficult to do so. Therefore, we can try testing 
if it follows
the $t$ distribution with increasingly smaller degrees of freedoms.

\input{tables/mc_pvals}

F

@@

Using simulation, we have shown that given a large enough sample of a time 
series, the block 
bootstrap KS test can appropriately fail to reject the null hypothesis when the
series follows the null distribution. In addition, when the marginal
distribution is not
the one hypothesized, the test is powerful. It requires a larger sample size 
than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
the method performs better as the temporal dependence gets weaker. We have also 
demonstrated possible applications of this method to precipitation and 
stock return data. This method can be used for any study where the goal is
to see if a time series follows a hypothesized distribution and the parameters
are unknown or unspecified.
